The Elements of Theses

### 2014-09-08 thesis/Vitae.tex
remove unpublished

%{\bf Selected Publications}
\begin{vitaesection}{Publications}
%\vspace{-0.5cm}
\item Michael Daniel Agun, Tao Yang, Wei Zhang. ``Asynchronous Source-side Deduplication for Cloud Data Backup''. {\it To be submitted for publication}.

\item Wei Zhang, Michael Daniel Agun, Tao Yang, Hong Tang. ``VM-Centric Snapshot Deduplication for Converged Cloud Architectures''. {\it Submitted to 2014 ACM Symposium on Cloud Computing (SoCC'14)}.

>>>>

%{\bf Selected Publications}
\begin{vitaesection}{Publications}
%\vspace{-0.5cm}
% \item Michael Daniel Agun, Tao Yang, Wei Zhang. ``Asynchronous Source-side Deduplication for Cloud Data Backup''. {\it To be submitted for publication}.

% \item Wei Zhang, Michael Daniel Agun, Tao Yang, Hong Tang. ``VM-Centric Snapshot Deduplication for Converged Cloud Architectures''. {\it Submitted to 2014 ACM Symposium on Cloud Computing (SoCC'14)}.
